\documentclass[10pt,a4paper,academicons]{altacv}

\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage[super]{nth}

\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

\setmainfont{Inter}

\hypersetup{colorlinks,linkcolor={cyan},citecolor={cyan},urlcolor={cyan}}

\definecolor{Vivid}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Vivid}
\colorlet{accent}{Vivid}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\newcommand{\googlescholar}[1]{\printinfo{\faGraduationCap}{#1}}
\newcommand{\stackoverflow}[1]{\printinfo{\faStackOverflow}{#1}}
\newcommand{\stackexchange}[1]{\printinfo{\faStackExchange}{#1}}
\newcommand{\home}[1]{\printinfo{\faHome}{#1}}

\DeclareNameAlias{author}{given-family}

\addbibresource{main.bib}

\AtEveryBibitem{\clearfield{pages}} 

\makeatletter
\def\mblx@yearfrom{-1000}
\def\mblx@yearto{3000}

\newrobustcmd*{\setcheckfromtorange}[2]{%
  \def\mblx@yearfrom{#1}%
  \def\mblx@yearto{#2}%
}

\defbibcheck{fromto}{%
  \iffieldint{year}
    {\ifnumless{\thefield{year}}{\mblx@yearfrom}
       {\skipentry}
       {\ifnumgreater{\thefield{year}}{\mblx@yearto}
          {\skipentry}
          {}}}
    {\skipentry}}
\makeatother

\newif\ifpublic{}

\publictrue{}
%\publicfalse{}

\begin{document}

\name{Siyu Wu}
\tagline{Love Math and Technique}
\personalinfo{%
  \email{\href{mailto:sywumath@gmail.com}{sywumath@gmail.com}}
  \location{Wuhan, Hubei Province, China}
  \homepage{\href{https://switwu.github.io}{Personal Page}}
  % \googlescholar{\href{https://scholar.google.com/citations?user=i2LNBfUAAAAJ}{Santiago Castro}}
  \github{\href{https://github.com/switwu}{Github}}
  % \twitter{\href{https://twitter.com/bryant1410}{bryant1410}}
  % \linkedin{\href{https://linkedin.com/in/santiagocastroserra}{santiagocastroserra}}
  % \stackoverflow{\href{https://stackoverflow.com/users/1165181/bryant1410}{bryant1410}}
  \stackexchange{\href{https://stackexchange.com/users/21523548/siyu-wu}{Stack Exchange}}
}

\begin{fullwidth}

\makecvheader{}

\end{fullwidth}

I'm a mathematics stident who is always curious about new techniques
and tools.

\cvsection[page1sidebar]{Education}

\cvevent{Bachelor's Degree in Pure Mathematics}{Wuhan University}{Sept. 2017 --- June. 2020}{Wuhan, Hubei Province}

\begin{itemize}
  \item In this period I had learnt many foundamental courses as well as computer programming related courses (such as machine learning, data structures and algorithm).
  \item I have learnt \TeX~and~\LaTeX~from this time.
    Based on this, I collated the exercise answers of  
    several books (functional analysis, algebra) and typeset them into PDF which are
    now accessible on my personal page.
\end{itemize}

\divider{}

\cvevent{Master's Degree in Pure Mathematics}{Wuhan University}{Sept. 2020 --- June 2023}{Wuhan, Hubei Province}

\begin{itemize}
  \item Advisor: \href{https://scholar.google.es/citations?user=KUH-_KIAAAAJ&hl=en}{Ao Weiwei}
  \item My research field is paraboilic and elliptic PDE.
    During extracurriculum time, I have learnt several skills such as
    Git, JavaScript.
\end{itemize}

\cvsection{Publications}

\href{https://scholar.google.com/citations?user=i2LNBfUAAAAJ}{523 citations and h-index 11 in Google Scholar.}

\cvsection{Programs}

\begin{itemize}
  \item Member of the \href{https://github.com/whutug}{WHU \TeX~User Group},
    participating in the development of thesis template of Wuha University (unofficial).
  \item A small tool: \href{https://title-case.github.io/}{Convert
    the String to Title Case},
    which is mainly used to process an arbitrary string and then strip
    useless characters at both ends, convert the string to title case.
\end{itemize}

(Resume last update: \today)

\end{document}
